### 2017-03-28 conclusion.tex
Fixed math typo

In this thesis we have explored the effects of SN feedback in the formation of
galaxies like our own.  Supernovae produce extremely hot ejecta
($T>10^8\;\mathrm{K}$) that rapidly shocks and expands against the significantly
under-pressured surroundings.  As massive stars form in clusters, these
individual SN remnants merge together, forming a superbubble.  These
superbubbles are much more effective at pushing and heating the ISM than an
equivalent amount of energy distributed as individual supernovae.  The primary
mechanism that sets the temperature of these superbubbles is the evaporation of
cold gas, driven by thermal conduction.  Thermal conduction becomes effective
above $10^5\;\mathrm{K}$, and strongly self-limits the temperature of
superbubbles to $\sim2-5\tims10^6\;\mathrm{K}$.  In this thesis, we have
developed a new model for SN feedback that takes into account these previously
ignored superbubble processes, and used that model to study the growth and
evolution of starforming galaxies.  This model allowed us to see when SN can
(and cannot!) regulate the flow of gas into and out of galaxies, where it may
forms stars.  Previous work \citep{Stinson2013,Hopkins2014} has suggested that
starforming galaxies could only regulate their growth if supernovae feedback was
heavily aided through early feedback from radiation pressure, stellar winds, and
UV heating.  With careful, physically motivated feedback models, we have now
shown that this is not the case:  the additional free parameters provided by
complex, numerically motivated early feedback are not necessary.  The primary
insight that this thesis provides is that the processes that mix feedback-heated
gas with the ISM (thermal evaporation in this case) are just as important as the
amount of energy provided by feedback.  Neither can be omitted if one wishes to
construct an accurate simulation of galaxy formation.

>>>>

In this thesis we have explored the effects of SN feedback in the formation of
galaxies like our own.  Supernovae produce extremely hot ejecta
($T>10^8\;\mathrm{K}$) that rapidly shocks and expands against the significantly
under-pressured surroundings.  As massive stars form in clusters, these
individual SN remnants merge together, forming a superbubble.  These
superbubbles are much more effective at pushing and heating the ISM than an
equivalent amount of energy distributed as individual supernovae.  The primary
mechanism that sets the temperature of these superbubbles is the evaporation of
cold gas, driven by thermal conduction.  Thermal conduction becomes effective
above $10^5\;\mathrm{K}$, and strongly self-limits the temperature of
superbubbles to $\sim2-5\times10^6\;\mathrm{K}$.  In this thesis, we have
developed a new model for SN feedback that takes into account these previously
ignored superbubble processes, and used that model to study the growth and
evolution of starforming galaxies.  This model allowed us to see when SN can
(and cannot!) regulate the flow of gas into and out of galaxies, where it may
forms stars.  Previous work \citep{Stinson2013,Hopkins2014} has suggested that
starforming galaxies could only regulate their growth if supernovae feedback was
heavily aided through early feedback from radiation pressure, stellar winds, and
UV heating.  With careful, physically motivated feedback models, we have now
shown that this is not the case:  the additional free parameters provided by
complex, numerically motivated early feedback are not necessary.  The primary
insight that this thesis provides is that the processes that mix feedback-heated
gas with the ISM (thermal evaporation in this case) are just as important as the
amount of energy provided by feedback.  Neither can be omitted if one wishes to
construct an accurate simulation of galaxy formation.
